---
title: "Project1Data607"
author: "Saloua Daouki"
date: "2023-09-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Packages and reading the .txt file

In this project, you\'re given a text file with chess tournament results where the information has some structure. Your
job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database)
with the following information for all of the players:
Player\'s Name, Player\'s State, Total Number of Points, Player\'s Pre-Rating, and Average Pre Chess Rating of Opponents
For the first player, the information would be:		

Gary Hua, ON, 6.0, 1794, 1605

```{r }
library(stringr)
library(readr)

url="https://raw.githubusercontent.com/SalouaDaouki/Project1Data607/master/tournamentinfo.txt"
df = readLines(url)
```

## Viewing the data

You can also embed plots, for example:

```{r pressure, echo=FALSE}
head(df)
```

## Modifying the data format:

```{r}
x0 = 0
x1 = unname(str_locate_all(pattern = '\\|', df[5])[[1]][1,1])
x2 = unname(str_locate_all(pattern = '\\|', df[5])[[1]][2,1])
x3 = unname(str_locate_all(pattern = '\\|', df[5])[[1]][3,1])
x4 = max(nchar(df))


seq1 = seq(5, 196, 3)
seq2 = seq(6, 196, 3)
group1 = df[seq1]
group2 = df[seq2]
```

```{r}
#group player names
name = substr(group1, x1 + 1, x2 - 2)
PlayerName = str_trim(name)

#group player state
state = substr(group2, x0, x1 - 1)
State = str_trim(state)

#group total points
totalpts = substr(group1, x2 + 1, x3 - 1)

#group pre-ratings
pre = substr(group2, x1 + 1, x2 - 1)
pre = str_extract(pre, ': *\\d{2,}')

#add each feature into dataframe
chess_df = data.frame(PlayerName, State)
chess_df$TotalPts = sprintf("%.1f", as.numeric(totalpts))
chess_df$PreRating = as.integer(str_extract(pre, '\\d{2,}'))

```

## Calculating the Average Pre Chess Rating of Opponents: 

1605 was calculated by using the pre-tournament opponents\' ratings of 1436, 1563, 1600, 1610, 1649, 1663, 1716, and
dividing by the total number of games played.

```{r}
opp = substr(group1, x3 + 1, x4)
opp = str_extract_all(opp, '\\b\\d{1,}')
opp = as.matrix(opp)

avgoppprerate = function(y, z){
  x = y[z]
  
  for (a in x) {
    rate = 0
    c = 0
    for (b in a) {
      c = c + 1
      rate = rate + chess_df$PreRating[as.numeric(b)]
    }
    rate = round(rate/c)
  }
  return(rate)
}

chess_df$AvgOppPreRating = apply(opp, 1, avgoppprerate)
```

## Viewing the new dataframe

```{r}
View(chess_df)
```

## Writing the new data frame as .csv file:

```{r}
write_csv (chess_df, "tournamentinfo.csv")
```

```{r}
csv_df = read_csv("https://raw.githubusercontent.com/SalouaDaouki/Project1Data607/master/tournamentinfo.csv")
```

```{r}
csv_df
```
